\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}

% Define custom colors
\definecolor{black}{RGB}{0,0,0}
\definecolor{gray}{RGB}{128,128,128}

% Set fonts
\renewcommand{\rmdefault}{phv}
\renewcommand{\sfdefault}{phv}

% Customize itemize environment
\setlist[itemize]{left=0em,labelsep=1em}
\renewcommand{\labelitemi}{\textbullet}

\begin{document}
\pagestyle{empty}

\begin{center}
    \textbf{\Huge Dao Le Minh} \\
    \vspace{2mm}
    Full-Stack Developer \\
    \vspace{2mm}
    \textcolor{gray}{Email: \textit{dao.minh@outlook.com}} \\
    \vspace{2mm}
    \textcolor{gray}{\textit{https://www.linkedin.com/in/le-minh-dao/}} \\
    \vspace{2mm}
    \textcolor{gray}{\textit{Ho Chi Minh City} | Vietnam}
\end{center}

\section*{Summary}
An experienced full-stack web developer looking forward to a challenging work environment. Skilled in creating visually appealing and user-friendly websites. A problem solver who delivers high-quality work, finding satisfaction in both feature functionality and problem-solving. My work style involves it digging into the core concepts and gaining a deep understanding of the problem before proposing solutions. A highly motivated individual who adeptly multitasks, prioritizes, and meets challenging deadlines, all while delivering superior performance standards.

\section*{Experience}
\subsection*{Jun 2023 -- Present | Back-end Developer | FPT Software | Ho Chi Minh City, Viet Nam}
\begin{itemize}
    \item Assisting in the development of web applications using micro-services and TypeScript.
    \item Contributing to database management tasks using MySQL.
    \item Working closely with the client to ensure product deliverables match standards.
\end{itemize}

\subsection*{June 2019 -- Feb 2023 | Full-stack Developer | Bitkub Blockchain Technology | Bangkok, Thailand}
\begin{itemize}
    \item Developed and maintained web applications using Node.JS and React.JS.
    \item Worked on database design and management using MySQL, Postgres and MongoDB.
    \item Implemented REST APIs for data communication.
    \item Collaborated with cross-functional teams to deliver high-quality software products.
    \item Troubleshooted and resolved application defects and performance issues.
\end{itemize}

\section*{Education}
\subsection*{Bachelor of Science, Information Technology | Stamford International University | Bangkok, Thailand | 2019--2023}
\begin{itemize}
    \item GPA: 3.86/4. With specialized certification in Software Engineering. Achieved High Distinctions.
\end{itemize}

\section*{Skills}
\begin{itemize}
    \item Programming Languages: JavaScript, TypeScript
    \item Web Technologies: Node.JS, Next.JS, HTML, CSS
    \item Databases: MySQL, Postgres, MongoDB, Redis.
    \item API: RESTful API
    \item Operating Systems: Linux, MacOS
    \item Tools: Git, Docker, Gitlab CI/CD, Jenkin.
\end{itemize}

\end{document}
